--
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction
I chose to use the 2013-2023-5-Checkouts-SPL dataset, and then filter through to
find all the checkouts of all Harry Potter series books, written by J. K.
Rowling. I love the Harry Potter series, and my family started listening to the
Harry Potter audiobooks during the summer of 2020, so I thought I could really
personally connect to this data. I was also particularly curious at the trend in
audiobook, ebook, and regular book checkouts and how they compare over the past
ten years.

### Summary Information
I found some really interesting aspects of this data! First off, I calculated
which year had the most amount of checkouts, what type of book it was, and how
many checkouts there were. In April of 2020, there were 1,894 checkouts of a Harry Potter
audiobook! From there, I wanted to see what percentage of checkouts were
audiobook, ebook, and regular book. Approximately 53.6% of checkouts over the
past ten years were audiobooks, 25% were regular books, and 21.3% were ebook.
The year with the least amount of regular book checkouts was

### The Dataset
The Seattle Public Library collected and published this data from what I can
tell. For the data I chose to use, the dates included were the year and month,
from January 2013 to January 2023. The kinds of books included audiobooks,
ebooks, and regular books, but the data overall included all varied kinds of
objects you can checkout from a library (movies, chargers, etc.). It also gave
you general subjects within each item, with tags such as "juvenile fiction,
wizards", and other words that could be used to further subdivide the data. The
data was collected to give the general public access to data that isn't usually
accessible. Most libraries don't offer this kind of data. Some ethical questions
we should consider when working with this data is am I using this data in a way
that is helpful to others? Another question that I don't think can be answered
is if there was any personal information also collected with each checkout. It's
an ethical question for the library: how much personal information is collected
when this data is collected? Some possible limitations with this data is that
there is no date, and some books have different titles despite ultimately being
the same book. For example, Harry Potter and the Sorcerer's Stone is listed as
a different book than "Harry Potter and the Sorcerer's Stone: Harry Potter
Series, Book 1", which is ultimately the same book just with different phrasing
of the title. I also have no way to measure how accurate or reliable this data
is.

### Graphic 1: Scatter Line Plot
I included this chart because I think it offers a great visual comparison
between the audiobook and other material types trends. You can see an incredible
spike in audiobooks the year that COVID hit. (I'm not implying causation but I
do think there is probably a correlation between the two.) If we look at trends
besides that one random spike in audiobooks, both ebooks and audiobooks have
been consistently vying for public popularity since about 2016. It makes me
wonder when the Nook, Kindle, or iPad became popular, as those are the main
technology you'd use when reading an ebook. There looks to be a consistent
number of book checkouts, though it's on average lower than that of ebook or
audiobook.

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1_example.R")}
```

### Graphic 2: Pie Chart

I included this graphic after the first because I truly believe it's a great way
visual in understanding just how significant audiobooks have become. An
astounding 53.6% of Harry Potter books that were checked out were audiobooks!
If you think about it, audiobooks are a great way to multitask. You can listen
while doing busybody jobs like cooking, cleaning, sitting around, drawing, etc.
Then again, this data could have also been skewed by that one spike that we saw
in the first graphic in April of 2020. I think that checkout must have been for
a school district's online English curriculum. However, compared to the first
chart, I think this pie chart offers fresh insight. In the first chart, I
believed that ebooks overall had a greater number of checkouts over the years,
but with this pie chart visual you can see that books actually had a higher
percentage of checkouts over the years. This could mean one of two things: one,
while ebooks have been on the rise, books still have a consistent amount of
subscribers, or two, ebooks became popular around 2016-2017, and books simply
have more years of data for regular customers than ebooks do.

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Graphic 3: Scatter Line Plot
I included this simple graphic because of the first two graphics. I wanted to
see, on its own, the audiobook trends to determine if the numbers have truly
been on the rise or if there was some kind of skewed number. With this chart
we can see much more clearly that there was a dramatic spike in 2020 (when
COVID hit), and then the trend has been generally lowered back down to normal
after 2020. I think for future analysis, I would like to compare a giant graph
of a monthly record of checkouts between audiobook, ebook, and book. I would
also love to analyze each of the books within the Harry Potter series and which
of them were each of the three material types.

``````{r, echo = FALSE, code = readLines("chart3_example.R")}
```


